Preliminary Thesis Defence

### 2013-12-14 PTD.tex
rename draft to PTD, remove redundant draft files, accidentally added redundant presentation files
clean for resubmission

\documentclass[a4paper,twopage]{report}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
\newcommand{\hlslot}[1]{\textit{#1}}%
\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage[authordate,backend=biber]{biblatex-chicago}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\title{Preliminary Thesis Defence\\~\\
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
\end{tabular}
}

@@

\begin{refsection}
\chapter{Introduction}
In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:

\begin{itemize}
\item Additional South African Evidence on Pensions and Child Growth (\ref{south-africa})
\item Replication: Surviving Andersonville (\ref{andersonville})
\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\ref{currency})
\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\ref{bitcoin})
\end{itemize}

@@

Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000, duflo2003}. These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren. A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women. This paper makes use of a Household Survey from 2008, 2012 and 2013. The survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009. As it stands now I have analysed the data from 2008 and 2012. The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.

Secondly, together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}. We were able to replicate all results from the paper, save for a few decimal numbers, which we have taken to be the result of rounding errors. However, replicating these numbers required us to take a number of unorthodox steps in our analysis. When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results. As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville. The authors however, aggregate these two. This leads to overstated magnitudes of the social ties of POWs. This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival. At this point our replication is quite complete. Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.

Thirdly, \textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium. It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium. I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainty. We thus gain information. I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.

Fourthly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. Bitcoin transactions are conducted using an electronic process called signing. I would like to study the role of Bitcoin in remittances. For this I would like to participate in building Bitcoin applications for the simple type of phones common in developing economies (sometimes referred to stupid phones). We could study the spread of bitcoin by looking at the downloads of the apps from regions, as well looking at how releasing the app in different languages evolves.

After this the papers follow, in the order listed above. A separate citations section is included for each chapter. For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs. In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole. I also mention some very preliminary ideas.

@@

\begin{refsection}
\chapter{Pensions and Child Growth in South Africa}
\label{south-africa}
\section*{Abstract}

In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.

I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients. This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.

@@

\section{Introduction}

This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
is very similar to \textcite{duflo2000, duflo2003}. The deviation from international standards \parencite{who2006child} for weight-for-height and length-for-age are computed as z-scores. These are then compared for different pension recipient status and gender.

@@

The South African pension is a interesting variable to measure income because of its criteria. Besides a maximum level of income, the only criterium is the age of a person. Because of this the status as a recipient is quite exogenous and there are few selection bias issues. The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.

Duflo finds evidence in South Africa's 1993 \href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated Household Survey} that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension. This is directly after the significant increase in the pension sum for blacks. The pension-eligibility age at this time was 60 for women and 65 for men.

This study deviates from the Duflo study in several ways. In 2008 and 2012, the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data. In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).

This happened in a few steps. As of July 16th 2008 men aged 63 and 64 were eligible for a pension. Men aged 61 and 62 became eligible in April 2009. Finally in January 2010, pension eligibility age was at 60 for all citizens.

Another deviation is the usage of WHO z-scores \parencite{who2006child} in stead of CDC z-scores \parencite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence, as long as we use the same standards consistently.

The main preliminary result is that the household effect (i.e.~having one or more recipients in the household) is very insignificant in the 2008 estimate. But in the 2012 estimate it is very significant.

\section{Data}

In this paper I use data from two sources. The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \parencite{who2006child}.

The main source of data is the NIDS. This survey collects data on a representative set of appproximately 10,000 South African households. The primary information variables that I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.

For adults, several variables measure the different amounts and sources of income. Among those, a variable for the adult receiving a state pension, and if so, how much. This is a numeric variable, the values of which lie very close together. For simplicity I have temporarily used this variable as a dummy.

The children's anthropometrics taken are, length/height, weight, and waist. Using these anthropometics and WHO growth standards, z-scores have been calculated. Unfortunately, the latest version of wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published. However, I have computed the length-for-age z-scores manually.

In 2006 the WHO published its standards for child growth. These standards are based on the scores of children from different ethnic populations in households which maintained a healthy lifestyle. The standards provide the means and standards deviations used. These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
p1 <- \hlfunctioncall{ggplot}(\hlfunctioncall{subset}(w1_child, w1_woman_60 == 1))
p1 <- p1 + \hlfunctioncall{aes}(w1_c_age_m, w1_zhfa, colour = \hlfunctioncall{factor}(w1_c_woman))
p1 <- p1 + \hlfunctioncall{stat_smooth}(method = \hlstring{"loess"}) + \hlfunctioncall{geom_point}()
p1
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 324 rows containing missing values (stat\_smooth).}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 263 rows containing missing values (stat\_smooth).}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 51 rows containing missing values (stat\_smooth).}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 638 rows containing missing values (geom\_point).}}\end{kframe}
\includegraphics[width=\maxwidth]{figure/r-p1}

\end{knitrout}

\section{Results}

Basic HAZ (2008)

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{summary}(w1_haz0)
\end{alltt}
\begin{verbatim}
## 
## Call:
## lm(formula = w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + 
##     w1_best_age_yrs, data = w1_child, subset = w1_c_age_m >= 
##     6 & w1_c_age_m <= 60)
## 
## Residuals:
##    Min     1Q Median     3Q    Max 
## -4.779 -1.036 -0.169  0.834  7.060 
## 
## Coefficients:
##                  Estimate Std. Error t value Pr(>|t|)    
## (Intercept)     -1.43e+00   1.44e-01   -9.87   <2e-16 ***
## w1_spen_w        2.32e-02   1.15e-01    0.20   0.8402    
## w1_spen_m        1.36e-01   1.72e-01    0.79   0.4281    
## w1_h_tinc        3.62e-05   9.99e-06    3.62   0.0003 ***
## w1_best_edu      1.63e-03   7.84e-03    0.21   0.8355    
## w1_best_age_yrs  7.61e-03   3.64e-03    2.09   0.0369 *  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 1.77 on 1436 degrees of freedom
##   (1936 observations deleted due to missingness)
## Multiple R-squared:  0.0134,	Adjusted R-squared:  0.00994 
## F-statistic: 3.89 on 5 and 1436 DF,  p-value: 0.00164
\end{verbatim}
\end{kframe}
\end{knitrout}

HAZ 2008, with 2012 eligiblity as an IV
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{summary}(tsls_w1w2_haz0)
\end{alltt}
\begin{verbatim}
## 
##  2SLS Estimates
## 
## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
## 
## Instruments: ~w2_spen_w + w2_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
## 
## Residuals:
##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
##  -4.990  -0.835  -0.050   0.000   0.788   7.070 
## 
##                   Estimate Std. Error t value Pr(>|t|)    
## (Intercept)     -1.172e+00  7.388e-02 -15.861  < 2e-16 ***
## w1_spen_w        1.748e-02  9.477e-02   0.184   0.8536    
## w1_spen_m       -1.374e-01  1.444e-01  -0.952   0.3414    
## w1_h_tinc        2.995e-05  5.606e-06   5.342 9.69e-08 ***
## w1_best_edu      2.410e-03  3.532e-03   0.682   0.4951    
## w1_best_age_yrs  4.127e-03  1.863e-03   2.215   0.0268 *  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 1.4889 on 4227 degrees of freedom
\end{verbatim}
\end{kframe}
\end{knitrout}

HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{summary}(tsls_w1w2_haz1)
\end{alltt}
\begin{verbatim}
## 
##  2SLS Estimates
## 
## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
## 
## Instruments: ~w2_spen_w + w2_spen_m_65 + w1_h_tinc + w1_best_edu + w1_best_age_yrs
## 
## Residuals:
##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
##  -4.990  -0.836  -0.050   0.000   0.786   7.040 
## 
##                   Estimate Std. Error t value Pr(>|t|)    
## (Intercept)     -1.173e+00  7.387e-02 -15.880  < 2e-16 ***
## w1_spen_w        8.576e-03  9.541e-02   0.090   0.9284    
## w1_spen_m       -9.189e-02  1.348e-01  -0.681   0.4956    
## w1_h_tinc        2.992e-05  5.605e-06   5.339 9.85e-08 ***
## w1_best_edu      2.443e-03  3.531e-03   0.692   0.4890    
## w1_best_age_yrs  4.092e-03  1.860e-03   2.200   0.0278 *  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 1.4885 on 4227 degrees of freedom
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{refsection}
\chapter{Replication: Surviving Andersonville}
\label{andersonville}
\textbf{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}

\section*{Abstract}
We replicate \textcite{costa2007surviving}. We are able to replicate all the result from the paper. The authors make a number of choices in order to arrive to the results published. We raise some concerns regarding some of these choices. For example, the authors treat the POWs of the two Andersonville camps as if they were in the same camp. This inflates size of the POWs social network, which is used as the explanatory variable. When we make choices which to us seem more defendable, we cannot, quantitatively and qualitatively, replicate the authors' results.

\section{Summary of the paper}
\textcite{costa2007surviving} try to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps. To examine the relationship the authors combine two datasets, a longitudinal dataset of Union Army soldiers and a cross-sectional dataset of the POW camp in Andersonville.

The empirical specification for the longitudinal data that measures the effect of the size of the network is as follows:

\begin{equation} \label{eq:ht}
h(t) = \exp ( \beta_1 F + \beta_2 I + \beta_3 M )
\end{equation}

where $h$ is hazard at time $t$, $F$ is the number of friends (=social network), $I$ are individual characteristics and $M$ macro camp conditions. The number of friends is measured as the number of POWs of the same company and varies by month due to deaths or camp transfers. As it might capture the lagged mortality of the group, the authors use as second strategy the initial number of friends as a time-invariant proxy. In addition, they instrument for the number of friends using the number of net camp transfers combined with a dummy indicating whether the POW was transferred to account for omitted variables. 
The specification for the Andersonville data in turn is a probit model:

\begin{align}
Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F) \label{s1} \\
Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j) \label{s1b} 
\end{align}

where equation \autoref{s1} examines quantity and \autoref{s1b} quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.

The longitudinal data indicates that POWs had special characteristics. For instance, they were likely to be volunteers, and from companies with more wounded or dead. POWs with more friends were typically US-born and wealthier while Irish and older men had less friends. Concerning survival rates, Kaplan-Meier hazard rates show that POWs captured later (after 1963 when the Union and the Confederate Army stopped exchanging POWs) have lower survival rates. They also show that survival rates were higher for POWs with 10 or more friends. In addition, the rates show that it takes 50 days until there is a divergence in survival between POWs with and without friends. The exponential function estimates that an additional friend leads to a 0.98 times lower mortality hazard. An increase in the number of friends from 0 to 5 (5 to 10), decreases the predicted probability of death from 0.31 to 0.28 (0.26) while a spline specification provides evidence that the effect is greatest for the first two friends. In addition, survival is more likely for POWs that had survived at least one or two months. Factors increasing mortality are the number of men in the camp, low rank, high age, and height among others. Insignificant variables are for instance wealth and marital status. There is no evidence for individual heterogeneity. The use of a Weibull specification indicates no duration dependence (toughen up effects). Interestingly though, a Cox model gives no significant effect of friends which the authors interpret as a result of their loss of power due to the small sample size. Robustness checks, including the IV approach and the effect of friends transferred in, confirms the significant effect of friends. Finally, the cross-sectional results provide evidence that having the same last name, being from the same town for smaller towns, ethnic similarity and having a sergeant or a higher rank in one's network are all important factors in raising survival probabilities which in turn shows that the quality of social networks matters.

In summary, Costa and Kahn are able to show that quantity and quality of social networks mattered for survival in civil war POW camps. Potential explanations for this are the sharing of scarce resources, moral support and protection from other prisoners.

\section{Data}
The raw data for the first part of the paper is extracted from the Union Army dataset readily accessible at \url{http://www.cpe.uchicago.edu}. This dataset draws information from censuses, medical records and military pension records linking military, socioeconomic and health information for nearly $40,000$ white males that served in the Union Army during the Civil War. For the second part, the Andersonville database is available at \url{http://www.itd.nps.gov/cwss} but only as a ``searchable version'', which allows viewing the information for one soldier at a time, and more convenient formats are not readily available.

The datasets provided for the estimations alongside with the publication are already partially processed parts of the raw data available online. No clear guidance is given as to what steps were taken to go from the raw data to the files provided, and matching both things proved to be less than straightforward. In view of this, we decided to proceed with the replication using the files provided by the authors, pointing out along the way the cases where potential problems in them seemed likely given the raw data we observed. Taking those files as starting points, it is possible to reproduce the tables and graphs published in the paper, so in this sense we can say that the data set is complete. Originally, some of the data required by the published .do files was not included in the published data files, but the authors provided it promptly upon our request and added it subsequently to the online files of the publishing journal.

The data and .do files provided do not describe or label many of the variables used, nor does the limited variable description in the Appendix cover all of them. A very thorough description of the variables in the raw data set can be found at its online source, but the match between this and the variables in the files provided is not straightforward or complete, since some of them are already created by the authors from the raw data. The description of the data itself, mainly of the variables that are used most often, is succinct but adequate, with Table 1 and Table 2 presenting some relevant descriptive traits. Despite this, some attention should be drawn to the fact that some of the variables have a relevant share of missing values (only the highest number of observations is reported), a point that will be commented in detail later on.

\section{Stata code and interpretation}
All codes run to their full extent, and produce the estimations presented in the paper, with minor differences that we describe in detail below. The codes themselves are not commented at all and include plenty of estimations and specifications not included in the published paper, as well as unexplained data processing steps. No exporting commands were set up, or log files kept, which might be the root of some of the rounding and significance discrepancies we have found.

In what follows, all reproduced tables are presented with a comment on the differences found (in bold), whenever there were any.

\subsection{Tables}
Table 1: This table presents the means of most variables later used for estimation, dividing observations in POWs and NON POWs, to illustrate ex ante differences in observables between them.

>>>>

\documentclass[a4paper]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage[authordate,backend=biber]{biblatex-chicago}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\title{Preliminary Thesis Defense\\~\\
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
\end{tabular}
}

@@

\begin{refsection}
\chapter{Introduction}
In this Preliminary Thesis Defense I present the research projects that I intend to use for my PhD dissertation. These projects are titled:

\begin{itemize}
\item Additional South African Evidence on Pensions and Child Growth (\autoref{south-africa})
% \item Replication: Surviving Andersonville (\ref{andersonville})
\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{uncertainty})
\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{bitcoin})
\end{itemize}

@@

Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000child, duflo2003grandmothers}.
These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
This paper makes use of a Household Survey from 2008, 2012 and 2013. The 
urvey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
As it stands now I have analysed the data from 2008 and 2012.
The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
I will discuss this in \autoref{south-africa}.

% Furthermore, in \autoref{andersonville},
% together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
% We were able to replicate all results from the paper, save for a few decimal numbers,
% which we have taken to be the result of rounding errors.

% However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
% When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
% As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
% The authors however, aggregate these two.
% This leads to overstated magnitudes of the social ties of POWs.
% This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
% At this point our replication is quite complete.
% Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.

\textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium.
I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainty.
We thus gain information.
I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
This is done in \autoref{uncertainty}.

Lastly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. 
Bitcoin transactions are conducted using an electronic process called signing.
I would like to study the role of Bitcoin in remittances.
For this I would like to participate in building Bitcoin applications for the type of simple phones common in developing economies (sometimes referred to a stupid phones).
We could study the spread of bitcoin by looking at the downloads of the apps from regions,
as well looking at how releasing the app in different languages evolves.

After this the papers follow, in the order listed above.
A separate citations section is included for each chapter.
For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs.
In the end notes (\autoref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
I also mention some very preliminary ideas.

@@

\begin{refsection}
\chapter{Pensions and Child Growth in South Africa}
\label{south-africa}
\section*{Abstract}
In this paper I look at differences in child malnutrition levels depending on the gender of the recipient of income.

I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
This paper exploits the fact that the data set consists of two surveys,
which were done before and after the lowering of the pension eligibility age for men to the same age as women.

@@

\section{Introduction}
This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa.
The approach is very similar to \textcite{duflo2000child,duflo2003grandmothers}.
The difference from international standards \parencite[WHO Child Growth Standards]{who2006child} for weight-for-height and length-for-age are computed as z-scores.
These are then compared for different pension recipient status.

@@

The South African pension is a useful variable to measure income because of its criteria.
Besides a maximum level of income, the only criterium is the age of a person.
Because of this the status as a recipient is quite exogenous and there are few selection bias problems.
The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.

This study deviates from the Duflo study in several ways.
First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income, including pension recipient status.
Whereas Duflo uses age as a proxy for recipient status.
Secondly, between mid 2008 and the end of 2009 the pension age for men was gradualy lowered to sixty, which is at par with women.
Another deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child} in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}.
Since these have superseded the CDC charts, however this should not be of any consequence.

The main preliminary result is that the household effect (i.e. having one or more recipients in the household),
is very insignificant in the 2008 estimate.
But in the 2012 estimate it is very significant.

\section{Data}
In this paper I use data from two sources.
The first is the South African National Income Dynamics Survey \parencite[NIDS]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.

The main source of data is the NIDS.
This survey collects data on a representative set of appproximately 10,000 South-African households.
The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.

For adults several variables measure the different amounts and sources of income.
Among those, a variable if the adult receives a state pension, and if so, how much.
This is a numeric variable, the values of which lie very close together.
For simplicity I have temporarily used this variable as a dummy.

Children's anthropometrics are taken, these are length/height, weight, and waist.
Using these anthropometics and WHO growth standards, z-scores have been calculated.
Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
However, I have computed the length-for-age z-scores manually.

In 2006 the WHO published its standards for child growth \parencite{who2006child}.
These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
The standards provide the means and standards deviations used. 
These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.

\section{Analysis}
\label{analysis}
I perform three types of analysis.
The first analysis uses the Duflo method, whereby I compute the z-scores (using WHO in stead of CDC, this is of no consequence) and then compare based on living in the household with an of-pension-eligible adult.
Secondly, I use my computed z-scores and the data set provided variable which describes the actual pension received (or lack thereof).
Lastly, I use this state pension variable to evaluate the z-scores provided in the dataset.

The first type of analysis is almost identical to Duflo.
Using an internation set of standard anthropometrics for healthy children between 6 and 60 months old, I standarize observed anthropometrics.
I then construct a number of dummies of different ages and gender of the pension recipients.

In the second analysis, I use the same z-scores I calculated for the Duflo method.
However, here I use the state pension recipient variable provided by the NIDS data set.
For simplicity I change the numerical variable to a dummy variable (as the benefits are virtually identical this is without much loss of information).

This method uses the pre calculated z-scores from the data set and the state pension dummy.
Unfortunately the 2012 z-scores are missing except for height-for-age.
I therefore use only the height-for-age z-scores for the 2012 estimates.

In all of these methods the z-scores can be compared on a number of properties.
Firstly, the status of living in the same household as a state pension recipient or not is the first property to compare.
Secondly, when living with a recipient,the effects of male and female recipients can be compared.
Thirdly, the effects based on the gender of the child can be compared.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% UNCOMMENT TO INCLUDE THE ANDERSONVILLE CHAPTER!!!!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{andersonville.tex}

\begin{refsection}
\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
\label{uncertainty}
\section*{Abstract}
\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
The self-fullfilling currency attack model which they propose thus has the suprising feature,
that with the introduction of risk perceptions, the multiple equilibria region, thus seems to solve to a single equilibrium.
It is my contention that this is not a surpising result, since the risk factor, replaces a previous existant, Knightian uncertainty, effectively increasing the body of knowledge.
Furthermore, the quantifiable risk only solves a certain part of the multiple equilibria region.
Lastly, if we replace the somewhat stange assumption of a bounded uniform distribution of risk perceptions,
with the more orthodox, normaly distribution, we cannot come to the same results.

\section{The Idea}
This paper addresses the issue multiple equilibria in models of currency attacks.
In situations of a currency peg, there is the possibility of a currency attack.
Investors will short the pegged currency, hoping the government will release the peg.
If a sufficiently large proportion of the market participates in this,
the cost of maintaining the peg for the government becomes too high,
which will lead to the government releasing the peg.
Currency attacks thus have a self-fulling nature,
which leads to a situation of multiple equilibria,
as described in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}.

In \textcite{morris1998unique} the authors describe such a model
and expand on it by introducting a second-order mechanism.
Hereby investors do not only look at the economics fundamentals of a currency,
but also at other investors' perceptions of these fundamentals.
This leads to a standard situation where there is a stable, unstable, and `ripe for attack' region (based on the economic fundamentals.

However, the authors then proceed to introduce a measure of risk around perceptions by investors.
Investors thus do not now the actual state of the fundamentals, but rather a distored form of it.
As a result, the investors' perception of other investors' perceptions are even more distorted.
Paradoxically, the leads to model being solvable to a unique equilibrium.

\section{The Model}

\section{The Results}

\section{The Issues}
By introduction the idea of perceptions of other investors' perceptions, the authors give a more complete picture of such a currency attack.
It is thus very surprising that the outcome of their more realistic model, correspond less to reality and the more incomplete models.
That is to say, the nature of currency attacks does seem to be characterised by multiple equilibria.
This explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.

In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor,
is the result of the fact that this risk factor eliminates the previously existing uncertainty.
In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk,
which is completer body of knowledge.
This view is enforced by the fact that,
the equilibrium is most pronounced when the risk factor ($\epsilon$) is minimised (i.e.~set equal to zero),
as the authors state themselves.
Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium,
is in fact the entire `ripe for attack' domain.

Also, the authors assume that the investors perception of other investors perception takes the form of a bounded uniform distribution.
It is unlikely that perceptions would best be described by a uniform distribution.
More importantly, it is unlikely that this distribution would be bounded, such as is assumed by the authors.
If we replace the bounded uniform distribution, with a normal distribution (which is unbounded),
then we cannot derive the same results.
